### 2016-11-16 src/intro.tex
writing local

In Section~\ref{sec:fixed} we discuss how the problem can be solved efficiently,
when $P$ and $D$ are given.
In Section~\ref{sec:uwcm} we describe a 2-approximation algorithm for the
unweighted variant of the problem.
In Section~\ref{sec:ucudcm} we describe a 2-approximation algorithm
for the uncapacitated variant of the problem. 
In Section~\ref{sec:cm} we present a 3-approximation
algorithm for the general problem. 
These are the first known approximation algorithms for any variant of the problem.
Finlay, in Section~\ref{sec:hardness}, we show that the problem is APX-hard.

>>>>

\todo{outline}
